Application of convolutional neural networks in optical text recognition to junk data filtering

### 2021-04-22 tex/paper/OMFI2021_Razumov_paper.tex
Reference was updated
Refs [6]-[9] was added. To be brushed.

\subsubsection*{Bag of words.}
The ``bag of words'' (BOW) model is a simplified representation of text used in natural language processing and information retrieval problems. Text is considered as a bag (multiset) of words or phrases in the case of combinations of terms, ignoring grammar and in some cases even word order, but preserving multiplicity in BOW. Each term (word or phrase) is assigned with a number. Then, text is defined by the vector $x=(x_1,..., x_N)^T$, where $N$ is the dimension from the finite dictionary $X_L$ contains the unique terms of the training sample. The following options to define $x_i$ are possible
\begin{enumerate}
\item Boolean weight equals $1,$ if element exists in a message or 
$0,$ else.
\item The number of occurrences of the $i$--th term in the text is 
$x_i = n_i.$
\item Term frequency is $x_i = n_i\slash\left(\sum\limits_{k=1}^i n_k\right).$
\end{enumerate}
{\color{red}\bf To determine $x_i$, the frequency of the term is selected.}

@@

\subsection{Aspects of algorithm implementation}
\subsubsection*{Microservice architecture.}
Since the service must operate under high loads, it is important to provide a robust architecture in which the failure of one component does not lead to the degradation of the entire system. The following client--server architecture is shown in figure\,\ref{fig:01}. Antispam daemon (mrasd) parses incoming messages and extracts text, images, and files from there. Since nested images and documents often contain junk data, it is also necessary to extract text from them. Then, documents are sent to the OCR service via a deferred redis queue, which extracts the text and stores the result in the redis cache.

@@

\subsubsection*{Brief review of the libraries}
Since services require high performance, the C++ language (stl 17, grpc, boost) is chosen as one of the most productive modern languages. For data analysis and training of the {\bf\color{red}AST model}, the Python 3 language and the utouch framework were utilized due to the high efficiency and the possibility of conducting parallel calculations, both on the CPU and on the GPU cores of the machine.

@@

\bibitem{Ref01} 
{\bf\color{red} Ref01}

\bibitem{Ref02} 
{\bf\color{red} Ref02}
\end{thebibliography}

>>>>

\subsubsection*{Bag of words.}
The ``bag of words'' (BOW) model is a simplified representation of text used in natural language processing and information retrieval problems. Text is considered as a bag (multiset) of words or phrases in the case of combinations of terms, ignoring grammar and in some cases even word order, but preserving multiplicity in BOW. Each term (word or phrase) is assigned with a number. Then, text is defined by the vector $x=(x_1,..., x_N)^T$, where $N$ is the dimension from the finite dictionary $X_L$ contains the unique terms of the training sample. The following options to define $x_i$ are possible
\begin{enumerate}
\item Boolean weight equals $1,$ if element exists in a message or 
$0,$ else.
\item The number of occurrences of the $i$--th term in the text is 
$x_i = n_i.$
\item Term frequency is $x_i = n_i\slash\left(\sum\limits_{k=1}^i n_k\right).$
\end{enumerate}
Third option was chosen to perform better convergence rate.

@@

\subsection{Aspects of algorithm implementation}
\subsubsection*{Microservice architecture.}
Since the service must operate under high loads, it is important to provide a robust architecture in which the failure of one component does not lead to the degradation of the entire system. The following client--server architecture is shown in figure\,\ref{fig:01}. Antispam daemon (mrasd) parses incoming messages and extracts text, images, and files from there. Since nested images and documents often contain junk data, it is also necessary to extract text from them. Then, documents are sent to the optical caracter recognition (OCR) service via a deferred redis queue, which extracts the text and stores the result in the redis cache.

@@

\subsubsection*{Brief review of the libraries}
Since services require high performance, the C++ language (stl 17, grpc, boost) is chosen as one of the most productive modern languages. Python 3 language and pyTorch framework were utilized for data analysis and training due to the high efficiency and the possibility of conducting parallel calculations, both on the CPU and on the GPU cores of the machine.

@@

\bibitem{Mikolov2013} 
Tomas Mikolov, Kai Chen, Greg Corrado, Jeffrey Dean.
2013. \emph{Efficient Estimation of Word Representations in Vector Space} //
arXiv:1301.3781v3

\bibitem{Bojanowski2017} 
Piotr Bojanowski, Edouard Grave, Armand Joulin, and Tomas Mikolov.
2017. \emph{Enriching Word Vectors with Subword Information} //
arXiv:1607.04606v2

\bibitem{Bommannavar2014}
Praveen Bommannavar, Alek Kolcz, Anand Rajaraman.
2014. \emph{Recall Estimation for Rare Topic Retrieval from Large Corpuses} //
2014 IEEE International Conference on Big Data

\bibitem{Yang2014}
Shuang Yang, Alek Kolcz, Andy Schlaikjer, Pankaj Gupta.
2014. \emph{Large-scale high-precision topic modeling on twitter} // Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining

\end{thebibliography}
